% LREC 2026 Example; 
% LREC Is now using templates similar to the ACL ones. 
\documentclass[10pt, a4paper]{article}

% custom commands
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{expex}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{amsmath}
%\usepackage{tikz-dependency}
\newcommand{\pg}[1]{{\color{blue}#1}}
\newcommand{\sy}[1]{{\color{red}#1}}
\newcommand{\drafttext}[1]{{\color{gray}#1}}
\newcommand{\corpus}[1]{{\color{gray}#1}}

% MAL mini-plot colours
\definecolor{malgreen}{HTML}{27ae60}
\definecolor{malred}{HTML}{e74c3c}
\definecolor{malgray}{HTML}{f39c12}
\definecolor{malblue}{HTML}{3498db}


% -----------------------------------

\usepackage{lrec2026} % this is the new style
% the 'review' option anonymizes the paper following submission guideline
% the 'final' option produces the camera ready version (non anonymized)
% default version is 'final', so use review option for submission

\title{Verifying the Menzerath-Altmann Law\\ in the Verbal Domain in 180 Languages}


\name{Pegah Faghiri\textsuperscript{1,2}, Kim Gerdes\textsuperscript{2}, Sylvain Kahane\textsuperscript{1,3}\thanks{Authors are listed in alphabetical order.}} 

\address{\textsuperscript{1}Paris Nanterre University, Modyco, CNRS~~
\textsuperscript{2}Paris-Saclay University, LISN, CNRS\\
\textsuperscript{3}IUF - Institut Universitaire de France \\
pfaghiri@parisnanterre.fr, kim.gerdes@universite-paris-saclay.fr, skahane@parisnanterre.fr\\}


\abstract{We present a large-scale evaluation of the Menzerath-Altmann law (MAL) in the verbal domain across 180 languages, using the Universal Dependencies (UD) treebank collection (v2.17). MAL predicts that as the number of constituents of a linguistic unit increases, their average size decreases. We propose a metric to estimate the MAL effect across corpora of widely varying sizes and define threshold-based categories to classify languages along a MAL preference cline. Crucially, we analyse the preverbal and postverbal domains separately, in addition to the standard bilateral MAL, and control for potential sampling bias by comparing results across language families (Indo-European vs.\ non-Indo-European) and syntactic types (VO, OV and no dominant order). Our results confirm MAL as a typologically widespread preference but not an absolute universal: several languages display a trivial or even opposite (anti-MAL) tendency. Furthermore, we uncover a significant asymmetry between the two sides of the verb: the MAL effect is stronger in the postverbal domain, while anti-MAL is stronger in the preverbal domain. VO languages tend to show a stronger MAL preference postverbally, whereas OV languages do so preverbally. These findings challenge the widespread assumption that length-based ordering constraints apply symmetrically on both sides of the verb and contribute new cross-linguistic evidence to the debate on the interaction between dependency length minimization and constituent size.
 \\ \newline \Keywords{Menzerath-Altmann law, quantitative typology, Universal Dependencies, verbal valency, constituent length, word order} }

\begin{document}

\maketitleabstract

\input{latex/section1-intro}
\input{latex/section2-MAL-background}
\input{latex/section3-constituent}
\input{latex/section4-metrics}
\input{latex/section4-42-decrease}
\input{latex/section5-results}
\input{latex/section5-52-zoom}
\input{section6-conclusion}

% \textbf{Appendices or supplementary material will be allowed ONLY in the final, camera-ready version, but not during submission, as papers should be reviewed without the need to refer to any supplementary materials.}

\section{Bibliographical References}\label{sec:reference}

\bibliographystyle{lrec2026-natbib}
\bibliography{lrec2026-example}

\section{Language Resource References}
\label{lr:ref}
\bibliographystylelanguageresource{lrec2026-natbib}
\bibliographylanguageresource{languageresource}

\appendix
\onecolumn
\section{MAL results for all languages}\label{app:all-languages}
%Removed for the reviewing process 
\input{latex/mal_miniplots_table}
\end{document}
