\section{Conclusion}\label{concl}
In this paper, we presented an exhaustive token-based evaluation of MAL in the verbal domain across the UD collection of 180 languages. We proposed a classification based on a metric that we defined in order to estimate the MAL effect for any given language satisfying a minimum threshold of occurrences for relevant configurations. We obtained a reliable classification of 131 languages, well distributed between IE and non-IE languages as well as between VO and OV languages. This classification allowed us to confirm MAL as a typologically widespread preference across the languages of the world, but importantly, it also showed that MAL is not an absolute universal principle. Not only did we find a number of languages in which MAL is absent or trivial, but we also found languages on the opposite end of the cline, displaying a clear MAL dispreference.

The second contribution of our study is the finding that, contrary to what has been previously assumed, MAL does not apply equally on both sides of the verb. MAL is stronger on the right side than on the left side, while Anti-MAL is stronger on the left side. This extends the findings of \citet{chen2022co}, who showed the co-effect of MAL and HCS to be universal on the postverbal side, by revealing that the picture is more complex on the preverbal side. This is a crucial finding, as it implies that length-based effects are not necessarily symmetric in the pre- and postverbal domains, contrary to the widespread assumption. Not only do our results show a clear difference between the pre- and postverbal domains, but they also show that VO and OV languages have different preference profiles in these domains. VO languages are more likely to show a strong MAL preference in the postverbal domain, while OV languages are more likely to show a strong MAL preference in the preverbal domain. Importantly, similar observations on the differences between pre- and postverbal domains have previously been made for length-based ordering preferences in individual languages such as Persian \citep{faghiriGlossa2020} or Mandarin \citep{Yao2018}. Moreover, there are alternative psycholinguistic production-based accounts of mirror-image word order preferences (SbL and LbS) in VO and OV languages that posit differences between the two domains. The latter claim that verbs exert strong influence over the constituents that follow them and, accordingly, assume that formal constraints are stricter in the postverbal domain than in the preverbal domain \citep{StallingsEtal}. Our study sheds new light on this ongoing debate.
All detailed results and interactive visualisations are available at \url{https://typometrics.elizia.net/menzerath/}. The full analysis code is released under a CC~BY~4.0 licence at \url{https://github.com/typometrics/UDW26-Menzerath}.
