\section{Introduction}

The current version of the Universal Dependencies (UD) collection of syntactic treebanks allows us to evaluate universal properties across a set of 180 languages \citeplanguageresource[v2.17,][]{ud2_17}. In this paper, we investigate the typological validity of the so-called Menzerath-Altmann law (MAL), which concerns the nature of complexity in linguistic units in terms of the relationship between the size of a given unit and the size of its components \citep{menzerath1928einige, menzerath1954architektonik, altmann1980prolegomena}. Roughly speaking, the greater the number of components of a given unit, the shorter their respective length. In the verbal domain, for instance, this implies that the length of verbal arguments decreases as the valency, or number of verbal dependents, increases \citep{macutek2017menzerath}. We also aim to propose a reliable metric to evaluate this hypothesis in the unbalanced UD collection, which contains annotated corpora of significantly different sizes---including the so-called LOL languages (``Literate, Official, and with Lots of users''), with millions of tokens, but also a number of corpora from less-studied languages with fewer than a thousand tokens. Furthermore, in order to make typologically relevant claims based on an \textit{ad hoc} language sample that was not designed for such purposes, we compare independent subsets of the collection separately to ensure that our conclusions are replicable beyond the sample as a whole and are not mere artefacts of sampling biases. First, with respect to language families, we consider the two main groups that are fairly equally represented in the collection, that is, Indo-European (IE) and non-Indo-European (non-IE) languages, separately. Second, we control for syntactic language types, namely OV, VO, and no dominant order (NDO), which we define using a token-based approach.\footnote{We defined the three types based on a VO score calculated for each language, as the ratio of the \texttt{obj} relations with a nominal object occurring after the verb. We labelled VO languages with a score greater than 0.67 (that is, languages in which the VO order is at least twice more widespread than OV), and OV languages with a score less than 0.33.}

Another important contribution of our study is that we examine preverbal and postverbal domains separately. That is, in addition to our general (or combined) MAL metrics, we calculate two separate sets of metrics for left/preverbal and right/postverbal arguments, respectively LMAL and RMAL. It is important to bear in mind that constituent size is known to obey other constraints. In particular there is the well-studied Dependency Length Minimization (DLM), which is one of the most widespread accounts of length-based word order preferences across languages \citep{Futrelletal2015,Ramon2004}. According to DLM, natural languages tend to favour orders that minimize dependency lengths. This results in a short-before-long preference (SbL) in the postverbal domain (typical of VO languages) and the reverse, that is a long-before-short preference (LbS), in the preverbal domain (typical of OV languages). In other words, the left and right sides of the verb are assumed to behave as mirror images, showing the same DLM effect but in opposite directions \citep{Hawkins2007}. Unlike DLM, however, MAL has a direction-free definition. Consequently, assuming that a direction-free length-based effect should apply similarly on each side of the verb, MAL is expected to hold equally on both sides. Relatedly, \citet{chen2022co} showed that the combined effect of MAL and HCS on the postverbal side is a cross-linguistic universal, but left the preverbal domain as an open question.

Our results show that MAL is a clearly widespread typological preference across the languages of the world. It is, however, not an absolute universal principle. Importantly, we find that while MAL is a strong cross-linguistic statistical preference, there are not only languages in which this preference is trivial, but also languages that display the opposite tendency. Furthermore, our results reveal a clear difference between the pre- and postverbal domains. On the one hand, the MAL preference is stronger in the postverbal domain; on the other hand, the anti-MAL preference is stronger in the preverbal domain. Importantly, our findings show that in the postverbal domain, VO languages are more likely to exhibit a strong RMAL preference, while, conversely, OV languages are more likely to exhibit a strong LMAL preference in the preverbal domain.

In the following, we first define MAL and briefly present the previous studies on which we build (Section~\ref{MAL}). Next, we present our data extraction method using the UD annotation scheme (Section~\ref{UD}) and the metrics we use in this study (Section~\ref{metrics} and Section~\ref{decrease}), while motivating our methodological choices. We then present our results (Section~\ref{results}), including a closer look at individual languages with unexpected behaviour (Section~\ref{zoom}), before concluding the paper (Section~\ref{concl}). The results for MAL, LMAL, and RMAL on the 180 languages of UD are given in Table \ref{table:annex} in Appendix A. An interactive version of all results is available at \url{https://typometrics.elizia.net/menzerath/}; the full analysis code is released under a CC~BY~4.0 licence at \url{https://github.com/typometrics/UDW26-Menzerath}.
