\subsection{Zooming into languages with unexpected behaviour}\label{zoom}
It is not possible to present the results for all the languages that contradict a universal MAL hypothesis. All the results are presented in Table \ref{tab:all-miniplots} in Appendix A. Here, we present some notable cases of Anti-MAL languages, as well as some cases of languages with inconsistent behaviour in the pre- and/or postverbal domains.

One interesting example of an Anti-MAL language is Old East Slavic, which not only has an Anti-MAL effect (that is, the mean length of constituents increases with the number of constituents), but moreover displays an Anti-MAL effect that grows stronger with the number of constituents (Figure~\ref{fig:OldEastSlavic}).

\begin{figure}[!ht]
\begin{center}
\begin{tikzpicture}
\begin{axis}[
  width=\columnwidth, height=0.65\columnwidth,
  xlabel={$\log(n)$}, ylabel={$\log(\mathrm{MAL}_n)$},
  xmin=-0.1, xmax=2.2,
  ymin=0.85, ymax=1.65,
  xtick={0, 0.6931, 1.0986, 1.3863, 1.6094, 1.7918, 1.9459, 2.0794},
  xticklabels={1, 2, 3, 4, 5, 6, 7, 8},
  grid=major, grid style={gray!30},
]
\addplot[only marks, mark=*, mark size=2pt, malblue] coordinates {
  (0.0000, 0.9814) (0.6931, 0.9840) (1.0986, 1.0382)
  (1.3863, 1.0833) (1.6094, 1.1662) (1.7918, 1.2971)
  (1.9459, 1.4054) (2.0794, 1.5513)
};
\addplot[no markers, malred, thick, domain=0:2.08] {0.255235*x + 0.850043};
\node[anchor=south west, font=\footnotesize] at (axis cs:0.02,0.87) {$\beta = -0.255$, $R^2 = 0.729$};
\end{axis}
\end{tikzpicture}
\caption{$\lambda$MAL(OldEastSlavic).}
\label{fig:OldEastSlavic}
\end{center}
\end{figure}

Starting with the preverbal domain, we find 29 Anti-LMAL languages, of which 17 are RMAL -- and they are mostly in the grey zone when bilateral MAL is considered. Two of these languages are noteworthy: Occitan (Romance, France) is MAL, while Naija (English-based pidgincreole, Nigeria) is Anti-MAL. Naija is also remarkable in that it is the most strongly Anti-LMAL language in our sample, following a near-perfect power law (Figures~\ref{fig:Naija-L} and~\ref{fig:Naija-R}).

\begin{figure}[!ht]
\begin{center}
\begin{tikzpicture}
\begin{axis}[
  width=\columnwidth, height=0.65\columnwidth,
  xlabel={$\log(n)$}, ylabel={$\log(\mathrm{LMAL}_n)$},
  xmin=-0.1, xmax=1.55,
  ymin=0.1, ymax=1.45,
  xtick={0, 0.6931, 1.0986, 1.3863},
  xticklabels={1, 2, 3, 4},
  grid=major, grid style={gray!30},
]
\addplot[only marks, mark=*, mark size=2pt, malblue] coordinates {
  (0.0000, 0.2515) (0.6931, 0.9103)
  (1.0986, 1.1697) (1.3863, 1.2369)
};
\addplot[no markers, malred, thick, domain=0:1.39] {0.733780*x + 0.309108};
\node[anchor=south west, font=\footnotesize] at (axis cs:0.02,0.12) {$\beta = -0.734$, $R^2 = 0.962$};
\end{axis}
\end{tikzpicture}
\caption{$\lambda$LMAL(Naija).}
\label{fig:Naija-L}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\begin{tikzpicture}
\begin{axis}[
  width=\columnwidth, height=0.65\columnwidth,
  xlabel={$\log(n)$}, ylabel={$\log(\mathrm{RMAL}_n)$},
  xmin=-0.1, xmax=1.25,
  ymin=1.1, ymax=1.35,
  xtick={0, 0.6931, 1.0986},
  xticklabels={1, 2, 3},
  grid=major, grid style={gray!30},
]
\addplot[only marks, mark=*, mark size=2pt, malblue] coordinates {
  (0.0000, 1.3024) (0.6931, 1.2012)
  (1.0986, 1.1578)
};
\addplot[no markers, malgreen, thick, domain=0:1.10] {-0.133124*x + 1.299963};
\node[anchor=south west, font=\footnotesize] at (axis cs:0.02,1.12) {$\beta = 0.133$, $R^2 = 0.994$};
\end{axis}
\end{tikzpicture}
\caption{$\lambda$RMAL(Naija).}
\label{fig:Naija-R}
\end{center}
\end{figure}


As for the postverbal domain, we find the following seven Anti-RMAL languages: Khoekhoe, Bambara, Egyptian, Old East Slavic, Western Armenian, Gothic, and Latin. It is worth noting that among them, four are corpora of ancient languages: Egyptian, Old East Slavic, Gothic, and Latin. Three are both Anti-MAL and Anti-LMAL as well (Bambara, Old East Slavic, and Latin),  the others are in the grey zone (for MAL, LMAL or both). In other words, none of the seven languages shows a MAL or an LMAL preference.  

Exploring the genetic and/or areal similarities and differences among these individual languages is beyond the scope of this paper, but it constitutes a necessary avenue for future research in understanding length-based effects across languages and linguistic domains.
