\section{Results}\label{results}
\subsection{MAL effect in the UD collection}\label{results1}
Out of the 186 languages available in our data, we calculated a $\beta$(1$\rightarrow\infty$) for 131. In this sample, we identify 62 languages with a MAL preference, 10 with an Anti-MAL preference, and 59 in the grey zone. Importantly, these three categories are fairly comparably represented across language families as well as across the main syntactic language types (Table~\ref{tab:MAL}). The only noticeable exception is that languages with no dominant order (NDO) are significantly more likely to be in the grey zone (and less likely to have a MAL preference) than VO or OV languages.\footnote{More precisely, the difference is significant between NDO and VO languages for the grey zone (respectively, 65\%  vs. 36\%, Fisher's Exact test p<0.05), as well as for the MAL type (25\% vs. 56\%, Fisher's Exact test p<0.05).}
 

\definecolor{rowred}{HTML}{F4CCCC}
\definecolor{rowyellow}{HTML}{FFF2CC}
\definecolor{rowgreen}{HTML}{D9EAD3}
\definecolor{rowgray}{HTML}{D9D9D9}
\definecolor{totalgreen}{HTML}{38761D}

\begin{table}[!ht]
\begin{center}
\begin{tabular}{l r r r}
\toprule
\textbf{Family /} & & & \\
\textbf{MAL type} & \textcolor{gray}{IE} & \textcolor{gray}{Non-IE} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
\rowcolor{rowred} Anti-MAL & 6 & 4 & \textcolor{totalgreen}{\textbf{10}} \\
\rowcolor{rowyellow} Gray zone & 22 & 37 & \textcolor{totalgreen}{\textbf{59}} \\
\rowcolor{rowgreen} MAL & 38 & 24 & \textcolor{totalgreen}{\textbf{62}} \\
\rowcolor{rowgray} Total & 66 & 65 & \textcolor{totalgreen}{\textbf{131}} \\
\bottomrule
\end{tabular}

\vspace{6pt}

\begin{tabular}{l r r r r}
\toprule
\textbf{VO/OV /} & & & & \\
\textbf{MAL type} & \textcolor{gray}{NDO} & \textcolor{gray}{OV} & \textcolor{gray}{VO} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
\rowcolor{rowred} Anti-MAL & 2 & 2 & 6 & \textcolor{totalgreen}{\textbf{10}} \\
\rowcolor{rowyellow} Gray zone & 13 & 20 & 26 & \textcolor{totalgreen}{\textbf{59}} \\
\rowcolor{rowgreen} MAL & 5 & 16 & 41 & \textcolor{totalgreen}{\textbf{62}} \\
\rowcolor{rowgray} Total & 20 & 38 & 73 & \textcolor{totalgreen}{\textbf{131}} \\
\bottomrule
\end{tabular}
\caption{MAL type per language family and VO/OV type.}
\label{tab:MAL}
\end{center}
\end{table}

For RMAL (postverbal domain) and LMAL (preverbal domain), we calculated $\beta$(1$\rightarrow\infty$) for 124 and 103 languages respectively, out of the total of 186 languages (Table~\ref{tab:FamLR} and Table~\ref{tab:HeadLR}). Interestingly, we find a clear difference between the pre- and postverbal domains. On the one hand, while we identify 62 languages (47\%) showing a MAL effect, there are 81 languages (79\%) showing a MAL effect in the postverbal domain (an RMAL effect), compared to only 39 languages (31\%) showing a MAL effect in the preverbal domain (an LMAL effect). In other words, 79\% of languages show a MAL effect in the postverbal domain, compared to 31\% in the preverbal domain, while the combined MAL effect is found in 47\% of languages. On the other hand, while we identify 10 Anti-MAL languages, there are 29 Anti-LMAL languages and 7 Anti-RMAL languages. In other words, 23\% of languages show an Anti-MAL effect in the preverbal domain, compared to 7\% in the postverbal domain, while 8\% show a bilateral Anti-MAL effect. 

\begin{table}[!ht]
\begin{center}
\begin{tabular}{l r r r}
\toprule
\textbf{Family} & & & \\
\textbf{RMAL type} & \textcolor{gray}{IE} & \textcolor{gray}{Non-IE} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
\rowcolor{rowred} Anti-MAL & 4 & 3 & \textcolor{totalgreen}{\textbf{7}} \\
\rowcolor{rowyellow} Gray zone & 5 & 10 & \textcolor{totalgreen}{\textbf{15}} \\
\rowcolor{rowgreen} MAL & 51 & 30 & \textcolor{totalgreen}{\textbf{81}} \\
\rowcolor{rowgray} Total & 60 & 43 & \textcolor{totalgreen}{\textbf{103}} \\
\bottomrule
\end{tabular}


\vspace{6pt}

\begin{tabular}{l r r r}
\toprule
\textbf{Family} & & & \\
\textbf{LMAL type} & \textcolor{gray}{IE} & \textcolor{gray}{Non-IE} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
\rowcolor{rowred} Anti-MAL & 15 & 14 & \textcolor{totalgreen}{\textbf{29}} \\
\rowcolor{rowyellow} Gray zone & 28 & 28 & \textcolor{totalgreen}{\textbf{56}} \\
\rowcolor{rowgreen} MAL & 20 & 19 & \textcolor{totalgreen}{\textbf{39}} \\
\rowcolor{rowgray} Total & 63 & 61 & \textcolor{totalgreen}{\textbf{124}} \\
\bottomrule
\end{tabular}
\caption{RMAL and LMAL per language family.}
\label{tab:FamLR}
\end{center}
\end{table}

We can therefore speak of both an RMAL bias and an Anti-LMAL bias---in other words, a preference for MAL in the postverbal domain and for Anti-MAL in the preverbal domain. Importantly, in our data, as with the combined MAL, the three LMAL and RMAL types are also fairly well distributed across language families (Table~\ref{tab:FamLR}). However, the same is not true for syntactic language types (Table~\ref{tab:HeadLR}). Nevertheless, the differences we observe in LMAL and RMAL types for OV and VO languages show a familiar pattern and are not surprising. 

\begin{table}[!ht]
\begin{center}
\begin{tabular}{l r r r r}
\toprule
\textbf{VO/OV} & & & & \\
\textbf{RMAL type} & \textcolor{gray}{NDO} & \textcolor{gray}{OV} & \textcolor{gray}{VO} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
\rowcolor{rowred} Anti-MAL & 3 & 2 & 2 & \textcolor{totalgreen}{\textbf{7}} \\
\rowcolor{rowyellow} Gray zone & 2 & 4 & 9 & \textcolor{totalgreen}{\textbf{15}} \\
\rowcolor{rowgreen} MAL & 14 & 10 & 57 & \textcolor{totalgreen}{\textbf{81}} \\
\rowcolor{rowgray} Total & 19 & 16 & 68 & \textcolor{totalgreen}{\textbf{103}} \\
\bottomrule
\end{tabular}


\vspace{6pt}

\begin{tabular}{l r r r r}
\toprule
\textbf{VO/OV} & & & & \\
\textbf{LMAL type} & \textcolor{gray}{NDO} & \textcolor{gray}{OV} & \textcolor{gray}{VO} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
\rowcolor{rowred} Anti-MAL & 2 & 4 & 23 & \textcolor{totalgreen}{\textbf{29}} \\
\rowcolor{rowyellow} Gray zone & 12 & 19 & 25 & \textcolor{totalgreen}{\textbf{56}} \\
\rowcolor{rowgreen} MAL & 4 & 15 & 20 & \textcolor{totalgreen}{\textbf{39}} \\
\rowcolor{rowgray} Total & 18 & 38 & 68 & \textcolor{totalgreen}{\textbf{124}} \\
\bottomrule
\end{tabular}
\caption{RMAL and LMAL per VO/OV type.}
\label{tab:HeadLR}
\end{center}
\end{table}

In the postverbal domain, we find that VO languages show a clearer bias towards RMAL than OV languages. In our sample of 103 languages with enough data on the postverbal domain, we have 68 VO, 16 OV, and 19 NDO languages.  Out of the 81 languages showing an RMAL effect, that is, with a significant positive RMAL effect in the postverbal domain, 57 are VO and 10 are OV languages. That is, 83\% of our VO languages show an RMAL effect compared to 63\% of our OV languages.
%Out of the 81 languages showing an RMAL effect, that is, with a significant positive MAL effect in the postverbal domain, 57 (79\%) are VO, compared to 10 (12\%) OV languages. 
Moreover, the Anti-RMAL preference is particularly rare among VO languages (2 out of 68 languages, 3\%, compared to 2 out of 16, 13\%, for OV languages). 

Conversely, in the preverbal domain, we observe a larger proportion of OV languages with an LMAL preference than VO languages: 39\% (15 out of 38) of OV languages show an LMAL effect, compared to 29\% (20 out of 68) of VO languages.
%(51\% vs.\ 38\% of the total of 39 LMAL languages). 
%Importantly, the Anti-LMAL preference is  more frequent in VO languages than in OV languages (79\% vs.\ 14\% of the total of 29 anti-LMAL languages). 
Importantly, the Anti-LMAL preference is much more frequent in VO languages than in OV languages: 34\% (23 out of 68) of VO languages show an Anti-LMAL effect compared to 11\% (4 out of 38) of OV languages.

In other words, on the one hand, VO languages are significantly more likely to show an RMAL preference than OV languages (83\% vs.\ 63\%), while also being less likely to show an Anti-RMAL preference (3\% vs.\ 13\%). On the other hand, OV languages are more likely to show an LMAL preference than VO languages (39\% vs.\ 29\%) and are also less likely to show an Anti-LMAL preference (11\% vs.\ 34\%). This latter observation is the most interesting, since the difference between the two language types is the largest. We observe that VO languages are roughly three times more likely to exhibit the Anti-LMAL preference than OV languages and this difference is statistically significant (Fisher's Exact test, p<0.01). 

These differences are indeed not surprising, given that an asymmetry in length-based effects between head-final/OV and head-initial/VO languages, for directional preferences such as DLM, is well established in the literature.
They are also in line with previous observations on the difference between the effect of phrasal length in pre- and postverbal domains \citep{faghiriGlossa2020}. We return to this point in our concluding remarks.


\subsection{MAL compliance in the UD collection}\label{results2}

Out of our 131 languages with a MAL effect, 79 show high MAL compliance, 23 show low MAL compliance, and 29 show medium MAL compliance (Table~\ref{tab:Dec1}). The mean MAL compliance ratios in these three groups are 0.90 (high), 0.13 (low), and 0.50 (middle), respectively. This classification is less strict (and hence less precise), resulting in a smaller number of borderline languages and a greater number of languages at the opposite end of the cline with low MAL compliance, compared to Anti-MAL languages.

In particular, we observe that NDO languages with a notably high number of languages in the grey zone (65\%), compared to VO and OV languages (36\% and 53\%, respectively), based on the MAL effect, show a more balanced distribution with MAL compliance types: 30\% are labeled middle, 45\% high and 25\% low. Borderline languages are still more frequent in NDO than in VO and OV languages, but the distribution of the three MAL compliance types is closer in NDO to what we observe for VO and OV languages, respectively, 19\% (middle), 64.5\% (high) and 16.5\% (low), and 24\% (middle), 60\% (high) and 16\% (low).

Importantly, the average compliance ratio values suggest that both MAL and Anti-MAL languages in our sample are clearly located at the edges of the cline. Based on these observations, we can expect the number of Anti-MAL languages to increase with a less strict measure and/or classification of the MAL effect.

\begin{table}[!ht]
\begin{center}
\begin{tabular}{l r r r r}
\toprule
 & \multicolumn{3}{c}{\textbf{MAL compliance}} & \\
\cmidrule(lr){2-4}
\textbf{Language family} & \textcolor{gray}{high} & \textcolor{gray}{middle} & \textcolor{gray}{low} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
IE & 38 & 16 & 12 & \textcolor{totalgreen}{\textbf{66}} \\
Non-IE & 41 & 13 & 11 & \textcolor{totalgreen}{\textbf{65}} \\
\rowcolor{rowgray} Total & 79 & 29 & 23 & \textcolor{totalgreen}{\textbf{131}} \\
\bottomrule
\end{tabular}

\vspace{6pt}

\begin{tabular}{l r r r r}
\toprule
 & \multicolumn{3}{c}{\textbf{MAL compliance}} & \\
\cmidrule(lr){2-4}
\textbf{VO/OV type} & \textcolor{gray}{high} & \textcolor{gray}{middle} & \textcolor{gray}{low} & \textcolor{totalgreen}{\textbf{Total}} \\
\midrule
NDO & 9 & 6 & 5 & \textcolor{totalgreen}{\textbf{20}} \\
OV & 23 & 9 & 6 & \textcolor{totalgreen}{\textbf{38}} \\
VO & 47 & 14 & 12 & \textcolor{totalgreen}{\textbf{73}} \\
\rowcolor{rowgray} Total & 79 & 29 & 23 & \textcolor{totalgreen}{\textbf{131}} \\
\bottomrule
\end{tabular}
\caption{MAL compliance per language family and VO/OV type.}
\label{tab:Dec1}
\end{center}
\end{table}

Note that we observe a similar pattern for RMAL and LMAL, which we do not present here for reasons of space.
%On the one hand, the MAL preference is stronger in the postverbal domain (about 80\% of the 103 languages for which we have a reliable RMAL metric - average compliance ratios for the three types are 0.95 (high), 0.18 (low) and 0.52 (middle), with respectively 84, 5 and 14 languages per type). On the other hand, the anti MAL preference is stronger in the preverbal domain (about 40\% of 124 languages for which we have a reliable LMAL metric - average compliance ratios for the three types are 0.91 (high), 0.11 (low) and 0.51 (middle), with respectively 57, 50 and 17 languages per type).

